### 2019-06-11 doc/chapters/challenge_stainless.tex
typo

In this chapter we look at the practical challenges that could occur by using Stainless.
Since Stainless is still in development and there is no 1.x release there might still be breaking changes and improvements fixing problems discribed now.

@@

Downgrading Bitcoin-S sbt version to 0.13.17 fixes the error but then it can not load some libraries only compiled for newer versions.
So this would take too much time to fix and changes the Bitcoin-S code unwantingly.

>>>>

In this chapter we look at the practical challenges that could occur by using Stainless.
Since Stainless is still in development and there is no 1.x release there might still be breaking changes and improvements fixing problems described now.

@@

Downgrading Bitcoin-S sbt version to 0.13.17 fixes the error but then it can not load some libraries only compiled for newer versions.
So this would take too much time to fix and changes the Bitcoin-S code inadvertent.
